Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-09-18 doc/RMD/mlg-mcg.Rmd
converting to joyplots to ridgeline plots
See here for details:
http://serialmentor.com/blog/2017/9/15/goodbye-joyplots

if (require("ggjoy")){
  ggplot(distplot, aes(x = dist, y = COMMS, group = COMMS, height = ..density..)) + 
    geom_joy(aes(lty = comparison, fill = mean)) + 
    theme_joy() + 
    theme(axis.text.y = element_text(hjust = 0)) + 
    viridis::scale_fill_viridis(option = "A", limits = quantile(distplot$dist, c(0.25, 0.75)))
}

>>>>

if (require("ggridges")){
  ggplot(distplot, aes(x = dist, y = COMMS, group = COMMS, height = ..density..)) + 
    geom_density_ridges(aes(lty = comparison, fill = mean)) + 
    theme_ridges() + 
    theme(axis.text.y = element_text(hjust = 0)) + 
    viridis::scale_fill_viridis(option = "A", limits = quantile(distplot$dist, c(0.25, 0.75)))
}
